The problem and promise of scale in multilayer animal social networks

### 2020-05-25 paper/manuscript.Rmd
use double output

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
  # github_document
  bookdown::pdf_document2:
     number_sections: true
     toc: false
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

## Landscape data and habitat classification
Land cover data were provided by the Newfoundland and Labrador Wildlife Division
[@Integrated_2013]. Available landcover classification included nine habitat
types at 30 m resolution. We reclassified the landcover types into three
categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
types, while forest habitat consisted of coniferous forest, conifer scrub,
broad leaf forest, and mixed-wood forest. Water habitat was excluded from all
subsequent analyses.

>>>>

---
title: The problem and promise of scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   github_document: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

## Landscape data and habitat classification
landcover data were provided by the Newfoundland and Labrador Wildlife Division
[@Integrated_2013]. Available landcover classification included nine habitat
types at 30 m resolution. We reclassified the landcover types into three
categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
types, while forest habitat consisted of coniferous forest, conifer scrub,
broad leaf forest, and mixed-wood forest. Water habitat was excluded from all
subsequent analyses.
